FAT-Pointer based range addresses

### 2024-02-25 papers/ISMM/FlexPointer/paper.tex
added base structure

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  The gap between application workloads and capacity of TLB is on the 
  rise. Previous work exploits this by physically contiguous 
  memory. Capability-based addressing in the CHERI architecture is 
  designed to improve hardware-level system security.
  These security mechanisms designed in place can also 
  behave as accelerators to standard user-space memory allocators. 
  The property of CHERI which is to use FAT-Pointers to store
  the upper and lower bounds can also be represented as ranges of 
  memory addresses which are physically contiguous. 
  <Talking about the results>.
\end{abstract}

@@

\ccsdesc[500]{Do Not Use This Code~Generate the Correct Terms for Your Paper}
\ccsdesc[300]{Do Not Use This Code~Generate the Correct Terms for Your Paper}
\ccsdesc{Do Not Use This Code~Generate the Correct Terms for Your Paper}
\ccsdesc[100]{Do Not Use This Code~Generate the Correct Terms for Your Paper}

%%
%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.
\keywords{Do, Not, Us, This, Code, Put, the, Correct, Terms, for,
  Your, Paper}

\received{20 February 2007}
\received[revised]{12 March 2009}
\received[accepted]{5 June 2009}

@@

\section{Related work}
\subsection{Huge Pages}
This is used to map a very large region of memory to a 
single entry. This small/large region of memory is physically
contiguous. Most implementations of huge pages are size
aligned, For example for the x86 architecture the huge pages 
size are 4KB, 2MB and 1GB pages. 
% \subsection{Tailored page sizes}
% TODO later
% \subsection{TLB coalescing}
% This leverages the default OS allocator behavior to pack
% multiple PTEs into a single TLB entry.

@@

>>>>

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  % Draft 1
  % The gap between application workloads and capacity of TLB is on the 
  % rise. Previous work exploits this by physically contiguous 
  % memory. Capability-based addressing in the CHERI architecture is 
  % designed to improve hardware-level system security.
  % These security mechanisms designed in place can also 
  % behave as accelerators to standard user-space memory allocators. 
  % The property of CHERI which is to use FAT-Pointers to store
  % the upper and lower bounds can also be represented as ranges of 
  % memory addresses which are physically contiguous. 
  % <Talking about the results>.
  % Draft 2
  The increasing disparity between application workloads and the capacity of Translation Lookaside Buffers (TLB) 
  has prompted researchers to explore innovative solutions to mitigate this gap. One such approach involves 
  leveraging physically contiguous memory to optimize TLB utilization. Concurrently, advancements in hardware-level 
  system security, exemplified by the Capability Hardware Enhanced RISC Instructions (CHERI) architecture, offer 
  additional opportunities for improving memory management and security.

 CHERI introduces capability-based addressing, a novel approach that enhances system security by associating capabilities 
 with memory pointers. These capabilities restrict access to memory regions, thereby fortifying the system against various 
 security threats. Importantly, the mechanisms implemented in CHERI for enforcing memory protection can also serve as 
 accelerators for standard user-space memory allocators. By leveraging capability-based addressing, memory 
 allocators can efficiently manage memory resources while ensuring robust security measures are in place.
\end{abstract}

@@

% \ccsdesc[500]{Do Not Use This Code~Generate the Correct Terms for Your Paper}
% \ccsdesc[300]{Do Not Use This Code~Generate the Correct Terms for Your Paper}
% \ccsdesc{Do Not Use This Code~Generate the Correct Terms for Your Paper}
% \ccsdesc[100]{Do Not Use This Code~Generate the Correct Terms for Your Paper}

%%
%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.
% \keywords{Do, Not, Us, This, Code, Put, the, Correct, Terms, for,
%   Your, Paper}

% \received{20 February 2007}
% \received[revised]{12 March 2009}
% \received[accepted]{5 June 2009}

@@

\section{Introduction}

\section{FAT-Pointer based range addresses}

\subsection{Overview}

\subsection{Range creation}

\subsection{Allocation with huge pages}

\section{Evaluation}

\section{Limitations}

\section{Related work}
Efficient memory management, particularly in the context of 
Translation Lookaside Buffer (TLB) optimization, has been a focal point of 
research and development within computer architecture. Various techniques have been 
proposed to mitigate TLB-related bottlenecks and improve overall system performance.

\subsection{Huge Pages}
This is used to map a very large region of memory to a 
single entry. This small/large region of memory is physically
contiguous. Most implementations of huge pages are size
aligned, For example for the x86 architecture the huge pages 
size are 4KB, 2MB and 1GB pages. 
% \subsection{Tailored page sizes}
% TODO later
% \subsection{TLB coalescing}
% This leverages the default OS allocator behavior to pack
% multiple PTEs into a single TLB entry.

@@

\section{Summary}
